\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-10-04 fig.tikz.tex
Update bttda formulation

\documentclass[tikz]{standalone}
\usepackage{pgfplots}
\begin{document}
\sffamily
\footnotesize
\begin{tikzpicture}
    \begin{axis}[
        width=\textwidth,
        height=0.6180\textwidth,
        scale only axis,
        xlabel={Time (ms)},
        ylabel={Potential ($\mu$V)},
        axis x line=middle,
	ylabel near ticks,
	xlabel near ticks,
        ymin=-5, ymax=8,
        enlarge x limits=false,
        enlarge y limits=false,
        smooth,
        every axis plot/.append style={very thick, accent1}, % Set the line color to accent1
        ytick={-5,0,5}, % Y-ticks at -5, 0, 5
        xtick={200,400,600}, % X-ticks at 200, 400, 600, 800
        axis line style={darkgray}, % Set the axis line color to darkgray
        tick style={darkgray}, % Set the tick color to darkgray
        tick label style={darkgray} % Set the tick label color to darkgray
    ]
    % ERP waveform using cubic splines for smooth connection
    \addplot[
        smooth,
        tension=0.5
    ] coordinates {
        (0, 0)     % Starting point
        (50, 0)    % Pre-P1
        (80, 2)    % P1
        (115, -3)  % N1
        (160, 3)   % P2
        (220, 1)   % N2
        (400, 7)   % P3
        (650, 1)   % LPP (Late Positive Potential)
        (800, 1)   % End point
    };

    % Annotations for the components
    \node[anchor=south, color=darkgray] at (axis cs:80,2) {P1};
    \node[anchor=north, color=darkgray] at (axis cs:115,-3) {N1};
    \node[anchor=south, color=darkgray] at (axis cs:160,3) {P2};
    \node[anchor=west, color=darkgray] at (axis cs:220,1) {N2};
    \node[anchor=south, color=darkgray] at (axis cs:400,7) {P3};
    \node[anchor=south west, color=darkgray] at (axis cs:650,1) {LPP};

    \end{axis}
\end{tikzpicture}
\end{document}

>>>>

\documentclass{standalone}
\usepackage{dissertation}
\input{chapters/bttda/tensorviz.tex}

\begin{document}
\begin{tikzpicture}[y=-1cm]
    \draw[help lines] (-3,-3) grid (20,6);
    \fill[red] (0,0) circle (2pt);

	  \begin{scope}[shift={(-0.0707, -0.0707)}]
      \MatrixSkewed{$\mat{A}_1$}{$r_1$}{$D_1$}{2}{1}
    \end{scope}
	  \begin{scope}[shift={(-0.1,0)}]
      \MatrixLeft{$\mat{A}_2$}{$r_2$}{$D_2$}{2}{1}
    \end{scope}
	  \begin{scope}[shift={(0,1.1)}]
      \MatrixBelow{$\mat{A}_3$}{$r_3$}{$D_3$}{1}{2}
    \end{scope}
    \TensorThree{$\ten{G}$}{}{}{}{1}{1}{1}

    \node at (2,.5){$=$};

	  \begin{scope}[shift={(3,-.5)}]
    \TensorThree{$\ten{X}^\prime$}{$D_1$}{$D_2$}{$D_3$}{2}{2}{2}
    \end{scope}

    \node at (6.5,.5){$=$};

	  \begin{scope}[shift={(7.5,-.5)}]
    \TensorThree{$\ten{X}$}{$D_1$}{$D_2$}{$D_3$}{2}{2}{2}
    \end{scope}

    \node at (11,.5){$-$};

	  \begin{scope}[shift={(12,-.5)}]
      \TensorThree{$\ten{\mathbfcal{E}}$}{$D_1$}{$D_2$}{$D_3$}{2}{2}{2}
    \end{scope}

\end{tikzpicture}
\end{document}
